r5r: rapid realistic routing on multimodal transport networks with R5 in R

### 2021-02-25 r-package/paper2020/paper2020.Rmd

While there are several open-source routing packages available for R, they either do not support public transport networks [@padgham2019dodgr], or focus on providing point-to-point routes rather than origin-destination travel time matrices [@morgan2019opentripplanner; @lovelace2019stplanr]. Most routing algorithms find paths to all points in the network while finding a single route. Storing these paths rather than computing them for one origin-destination pair at a time is orders of magnitude more efficient. To our knowledge, no R package exists that supports these efficient many-to-many queries for public transport networks.

>>>>

While there are several open-source routing packages available for R, they either do not support public transport networks [@padgham2019dodgr], or primarily focus on providing point-to-point routes rather than origin-destination travel time matrices [@morgan2019opentripplanner; @lovelace2019stplanr]. Most routing algorithms find paths to all points in the network while finding a single route. Storing these paths rather than computing them for one origin-destination pair at a time is orders of magnitude more efficient. To our knowledge, no R package exists that supports these efficient many-to-many queries for public transport networks.
